Effective multi-body SU($N$)-symmetric interactions of ultracold fermionic atoms on a 3-D lattice

### 2019-02-14 multi_body_interactions/papers/theory/reviews_NJP/referee_response_2.tex

  We hope that these additions help improve readers' interpretations
  of the numerical results in our manuscript.

\item Finally:

  \blue{Overall, the manuscript contains substantial and solid results
    and data on few-body spectra of SU(N) atoms and can be quite
    useful to future studies on these atoms. I recommend the
    publication of the manuscript in NJP after my concerns above are
    addressed.}

  We thank the referee for their consideration

  We thank the referee for remarking that our manuscript ``contains
  substantial and results'', and hope that our results will indeed be
  ``quite useful to future studies''.  The referee has brought up some
  fair questions and suggestions, which we have addressed by
  additional discussion and a new appendix in our manuscript.  We hope
  that these changes have addressed the referee's concerns to a
  satisfactory degree, deeming our manuscript suitable for publication
  in New Journal of Physics.

### 2019-02-18 multi_body_interactions/papers/theory/paper.tex
final versions of responses and revisions to NJP

\begin{table}
  \centering
  \caption{\footnotesize Low-excitation eigenvalues of $M$-body
    Hamiltonians $H_M$.  Many-body energy eigenstates are labeled by
    the nuclear spins they occupy (i.e.~$\N$ with $N\equiv\abs{\N}$)
    and whether they are in an orbital ground ($0$), singly-excited
    symmetric ($+$), or singly-excited asymmetric ($-$) state.  The
    corresponding $N$-body eigenvalues $E_{NX}^{(M)}$ of $H_M$ are
    given in terms of the coefficients $U_{MX}$ as appearing in
    \eqref{eq:H_M}, in addition to the $M$-body eigenvalues
    $E_{MX}^{(M)}$.}
  \label{tab:eigen}
  \begin{tabular}{c|c}
    Eigenstate
    & $H_M$ eigenvalue \\ \hline\hline
    $\ket{\N,0}$
    & $M! {N \choose M} U_{M,\g}$ \\ \hline
    $\ket{\N,+}$
    & $M! {N-1 \choose M} U_{M,\g}
    + \p{M-1}! {N-1 \choose M-1} \p{U_{M,+} + U_{M,-}}$ \\ \hline
    $\ket{\N,-}$
    & $M! {N-1 \choose M} U_{M,\g}
    + \p{M-1}! {N-1 \choose M-1} U_{M,+}
    - \p{M-2}! {N-2 \choose M-2} U_{M,-}$ \\ \hline\hline
    $\ket{\N,0}$
    & ${N \choose M} E_{M,0}^{(M)}$ \\ \hline
    $\ket{\N,+}$
    & ${N-1 \choose M} E_{M,0}^{(M)}
    + {N-1 \choose M-1} E_{M,+}^{(M)}$ \\ \hline
    $\ket{\N,-}$
    & ${N-1 \choose M} E_{M,0}^{(M)}
    + M^{-1} \sp{{N-1 \choose M-1} - {N-2 \choose M-2}} E_{M,+}^{(M)}
    + \sp{\p{1 - M^{-1}} {N-1 \choose M-1}
      + M^{-1} {N-2 \choose M-2}} E_{M,-}^{(M)}$
  \end{tabular}
\end{table}

@@

Identifying peaks in excitation spectra such as in figure
\ref{fig:sweep} constitutes a measurement of many-body excitation
energies, which was performed in ref.~\cite{goban2018emergence} to
detect signatures of effective multi-body interactions.  Figure
\ref{fig:shifts} shows a comparison between
\begin{enumerate*}
\item experimental measurements of the many-body excitation energies
  $\Delta_{NX}$ for all $\p{N,X}\in\set{3,4,5}\times\set{+,-}$ at
  various mean lattice depths $\U$, and
\item the corresponding values of $\Delta_{NX}$ predicted by the
  low-energy effective theory at different orders in the coupling
  constants.
\end{enumerate*}
A known source of error in our effective theory comes from neglecting
the inter-site matrix elements of all Hamiltonians.  This error is
discussed in Appendix \ref{sec:error}, and leads to theoretical
uncertainties represented by error bars on the $\O\p{G^3}$ theory in
figure \ref{fig:shifts}.  A summary of figure \ref{fig:shifts} is
provided in figure \ref{fig:shifts_summary}.  We note that many-body
interaction energy shifts are smaller for asymmetric ($-$) states than
symmetric ($+$) ones due to the competition between contributions of
opposite sign in the asymmetric case (see rows 2 and 3 of table
\ref{tab:eigen}).

The results in figures \ref{fig:shifts} and \ref{fig:shifts_summary}
highlight a few important points about ultracold, high-density
${}^{87}$Sr experiments and our low-energy effective theory.  First,
these experiments exhibit clear signatures of multi-body interactions,
as evidenced by a stark disagreement between the observed many-body
excitation energies $\Delta_{NX}$ and those that are predicted by the
two-body $\O\p{G}$ theory.  Multi-body interactions are thus crucial
for understanding these high-density experiments in the context of a
single-band Hubbard model, which naturally arises in the
zero-temperature limit when all atoms occupy their motional ground
state.  Second, the inter-atomic interactions in these experiments are
strong enough to require going beyond leading order for the
description of multi-body interactions in the low-energy effective
theory.  The formally small quantities organizing our perturbation
theory are two-body ground-state interaction energies (proportional to
the couplings $G_X$) divided by the spectral gap of the single-atom
Hamiltonian $H_0$.  These reduced (dimensionless) interaction energies
vary from $\sim0.05-0.15$ in the parameter regimes of the ${}^{87}$Sr
experiments considered here (see Appendix \ref{sec:pert_params}).  As
experiments begin to work with more atoms and different lattice
depths, therefore, reliably predicting interaction energies may
require going to yet higher orders in perturbation theory.  Due to a
combinatorial explosion of the number of diagrams which appear at
increasing orders in the effective theory, however, we need more
systematic methods to compute effective multi-body Hamiltonians at
fourth order.  In any case, we are agnostic as to whether such a
calculation would provide better agreement between experiment and
theory without first performing a detailed analysis of systematic
errors.

@@

The perturbative effective theory developed in Section
\ref{sec:low_energy} is organized in powers of the coupling constants
$G_X$.  The formally small, dimensionless quantities for this
perturbation theory are the two-body interaction energies $K G_X$,
where $K$ is a ground-state two-body overlap integral and $G_X$ is a
coupling constant, divided by the spectral gap $\Delta$ of the
non-interacting Hamiltonian $H_0$.  The quantities $K$, $G_X$, and
$\Delta$ all depend on the lattice depth $\U$.  Figure
\ref{fig:pert_params} shows these parameters for the case of
${}^{87}$Sr atoms with $X\in\set{\g\g, \e\g_-, \e\g_+, \e\e}$ at
lattice depths $\U\in\sp{30,80}E_{\t{R}}$, where
$E_{\t{R}}\approx3.5\times2\pi~\t{kHz}$ is the lattice photon recoil
energy of the atoms.  The fact that these perturbative parameters grow
with increasing lattice depth $\U$ is a consequence of the fact that
the overlap integral $K$ grows faster with $\U$ than the spectral gap
$\Delta$.  In the case of a harmonic trap with angular frequency
$\omega$, for example, these parameters would be
\begin{multline}
  \f{K_{\t{HO}} G_X}{\omega}
  = \f{G_X}{\omega} \int \d^3 x~\abs{\phi_{\t{HO}}}^4
  = \f{G_X}{\omega} \sp{\int \d x~
    \abs{\p{\f{\mA\omega}{\pi}}^{1/4} e^{-\mA\omega x^2/2}}^4}^3 \\
  \sim \f1{\omega}
  \sp{\omega \int\f{\d\p{\sqrt\omega x}}{\sqrt\omega}
    ~\abs{e^{-\mA\omega x^2/2}}^4}^3
  \propto \sqrt{\omega},
\end{multline}
where we assumed that the coupling constants $G_X$ vary weakly with
$\omega$.  While this result may seem to suggest that the low-energy
effective theory should become better at smaller lattice depths,
smaller lattice depths also result in increased theoretical
uncertainties from the growing relevance of the inter-site effects
discussed in Appendix \ref{sec:error}.

@@

When restricted to the subspace of at most one orbital excitation per
lattice site, the $M$-body Hamiltonians of the low-energy effective
theory developed in Section \ref{sec:low_energy} can be written in the
form
\begin{align}
  H_M = \sum_{\abs{\set{\mu_j}}=M}
  \p{U_{M,\g} \n_{\mu_1,\g} \n_{\mu_2,\g}
    + U_{M,+} \n_{\mu_1,\e} \n_{\mu_2,\g}
    + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
    \c_{\mu_2,\g} \c_{\mu_1,\e}}
  \prod_{\alpha=3}^M \n_{\mu_\alpha,\g},
\end{align}
where the coefficients can be expanded as
$U_{MX} = \sum_p U_{MX}^{(p)}$ with terms $U_{MX}^{(p)}$ at order $p$
in the coupling constants $G_Y$.  The terms $U_{MX}^{(p)}$ can be
determined from the $M$-body $p$-order Hamiltonians $H_M^{(p)}$
derived in section \ref{sec:low_energy}, i.e.~in \eqref{eq:H_2},
\eqref{eq:H_3_2}, \eqref{eq:H_3_3}, and \eqref{eq:H_4_3}.  For the
effective 2-, 3-, and 4-body Hamiltonians through third order in the
coupling constants, the coefficients are
\begin{align}
  U_{2,\g} = \f12 \alpha_2^{(1)} G_\g,
  &&
  U_{2,+} = \alpha_2^{(1)} G_+,
  &&
  U_{2,-} = \alpha_2^{(1)} G_-,
\end{align}
\begin{align}
  U_{3,\g}^{(2)} = - \alpha_3^{(2)} G_\g^2,
  &&
  U_{3,+}^{(2)} = - \alpha_3^{(2)} G_+ \p{G_+ + 2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(2)} = - \alpha_3^{(2)} G_- \p{2 G_+ + G_- + 2 G_\g},
\end{align}
\begin{align}
  U_{3,\g}^{(3)}
  = \p{\alpha_3^{(3)} - \alpha_5^{(3)}} 2 G_\g^3
  - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}} G_\g^3,
\end{align}
\begin{align}
  U_{3,+}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} \p{G_+^3 + 4 G_+^2 G_\g
    + G_+ G_-^2 + G_+ G_\g^2 + G_-^3 + G_-^2 G_\g} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  \p{G_+^3 + G_+^2 G_\g + G_+ G_-^2 + G_+ G_\g^2 + G_-^2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} G_- \p{3 G_+^2
    + 2 G_+ G_- + 8 G_+ G_\g + 3 G_- G_\g + G_\g^2} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 2 G_+ G_- + 2 G_+ G_\g + G_-^2 + G_\g^2},
\end{align}
\begin{align}
  U_{4,\g}^{(3)}
  = \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} G_\g^3
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} 2 G_\g^3,
\end{align}
\begin{align}
  U_{4,+}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_+ G_\g \p{G_+ + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_+ \p{G_+^2 + 2 G_+ G_\g + 5 G_\g^2},
\end{align}
\begin{align}
  U_{4,-}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_- G_\g \p{2 G_+ + G_- + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 3 G_+ G_- + 4 G_+ G_\g + G_-^2
    + 2 G_- G_\g + 5 G_\g^2},
\end{align}
In terms of the spatial overlap integrals defined in \eqref{eq:K_klmn}
and \eqref{eq:K}, the prefactors $\alpha_X^{(p)}$ on the coefficients
$U_X^{(p)}$ are
\begin{align}
  \alpha_2^{(1)} \equiv K,
  &&
  \alpha_3^{(2)} \equiv \sum_{n>0} \f{K_n^2}{E_n},
  &&
  \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
  \f{K_{\ell m} K^m_n K_{\ell n}}{E_{\ell m} E_{\ell n}},
\end{align}
\begin{align}
  \alpha_{4,1}^{(3)}
  \equiv \sum_{\substack{m\ge0\\n>0}} \f{K_{mn} K_m K_n}{E_{mn} E_n},
  &&
  \alpha_{4,2}^{(3)}
  \equiv \sum_{m,n>0} \f{K_m K^m_n K_n}{E_m E_n},
  &&
  \alpha_{4,3}^{(3)}
  \equiv K \sum_{m+n>0} \f{K_{mn}^2}{E_{mn}^2},
\end{align}
\begin{align}
  \alpha_5^{(3)}
  \equiv  K \sum_{n>0} \f{K_n^2}{E_n^2}.
\end{align}

>>>>

\begin{table}
  \centering
  \caption{\footnotesize Low-excitation eigenvalues of $M$-body
    Hamiltonians $H_M$.  Many-body energy eigenstates are labeled by
    the nuclear spins they occupy (i.e.~$\N$ with $N\equiv\abs{\N}$)
    and whether they are in an orbital ground ($0$), singly-excited
    symmetric ($+$), or singly-excited asymmetric ($-$) state.  The
    corresponding $N$-body eigenvalues $E_{NX}^{(M)}$ of $H_M$ are
    given in terms of the coefficients $U_{MX}$ as appearing in
    \eqref{eq:H_M} (first three rows), in addition to the $M$-body
    eigenvalues $E_{MX}^{(M)}$ (last three rows).}
  \label{tab:eigen}
  \begin{tabular}{c|c}
    Eigenstate
    & $H_M$ eigenvalue ($M\le N$) \\ \hline\hline
    $\ket{\N,0}$
    & $M! {N \choose M} U_{M,\g}$ \\ \hline
    $\ket{\N,+}$
    & $M! {N-1 \choose M} U_{M,\g}
    + \p{M-1}! {N-1 \choose M-1} \p{U_{M,+} + U_{M,-}}$ \\ \hline
    $\ket{\N,-}$
    & $M! {N-1 \choose M} U_{M,\g}
    + \p{M-1}! {N-1 \choose M-1} U_{M,+}
    - \p{M-2}! {N-2 \choose M-2} U_{M,-}$ \\ \hline\hline
    $\ket{\N,0}$
    & ${N \choose M} E_{M,0}^{(M)}$ \\ \hline
    $\ket{\N,+}$
    & ${N-1 \choose M} E_{M,0}^{(M)}
    + {N-1 \choose M-1} E_{M,+}^{(M)}$ \\ \hline
    $\ket{\N,-}$
    & ${N-1 \choose M} E_{M,0}^{(M)}
    + M^{-1} \sp{{N-1 \choose M-1} - {N-2 \choose M-2}} E_{M,+}^{(M)}
    + \sp{\p{1 - M^{-1}} {N-1 \choose M-1}
      + M^{-1} {N-2 \choose M-2}} E_{M,-}^{(M)}$
  \end{tabular}
\end{table}

@@

Identifying peaks in excitation spectra such as in figure
\ref{fig:sweep} constitutes a measurement of many-body excitation
energies, which was performed in ref.~\cite{goban2018emergence} to
detect signatures of effective multi-body interactions.  Figure
\ref{fig:shifts} shows a comparison between
\begin{enumerate*}
\item experimental measurements of the many-body excitation energies
  $\Delta_{NX}$ for all $\p{N,X}\in\set{3,4,5}\times\set{+,-}$ at
  various mean lattice depths $\U$, and
\item the corresponding values of $\Delta_{NX}$ predicted by the
  low-energy effective theory at different orders in the coupling
  constants.
\end{enumerate*}
A known source of error in our effective theory comes from neglecting
the inter-site matrix elements of all Hamiltonians.  This error is
discussed in Appendix \ref{sec:error}, and leads to theoretical
uncertainties represented by error bars on the $\O\p{G^3}$ theory in
figure \ref{fig:shifts}.  A summary of figure \ref{fig:shifts} is
provided in figure \ref{fig:shifts_summary}.  We note that many-body
interaction energy shifts are smaller for asymmetric ($-$) states than
symmetric ($+$) ones due to the competition between contributions of
opposite sign in the asymmetric case (see rows 2 and 3 of table
\ref{tab:eigen}, where as a consequence of positive scattering lengths
in the case of $^{87}$Sr, all $U_{MX}$ for fixed $M$ have the same
sign).  This competition is a many-body analogue of the two-body case
with a competition between direct and exchange terms in the
interaction energies of singly-excited states.

The results in figures \ref{fig:shifts} and \ref{fig:shifts_summary}
highlight a few important points about ultracold, high-density
${}^{87}$Sr experiments and our low-energy effective theory.  First,
these experiments exhibit clear signatures of multi-body interactions,
as evidenced by a stark disagreement between the observed many-body
excitation energies $\Delta_{NX}$ and those that are predicted by the
two-body $\O\p{G}$ theory.  Multi-body interactions are thus crucial
for understanding these high-density experiments in the context of a
single-band Hubbard model, which naturally arises in the
zero-temperature limit when all atoms occupy their motional ground
state.  Second, the inter-atomic interactions in these experiments are
strong enough to require going beyond leading order for the
description of multi-body interactions in the low-energy effective
theory.  The formally small quantities organizing our perturbation
theory are two-body ground-state interaction energies (proportional to
the couplings $G_X$) divided by the spectral gap of the single-atom
Hamiltonian $H_0$.  These reduced (dimensionless) interaction energies
vary from $\sim0.05-0.15$ in the parameter regimes of the ${}^{87}$Sr
experiments considered here (see Appendix \ref{sec:pert_params}).  As
experiments begin to operate at higher atom densities with amplified
interaction effects, reliably predicting interaction energies may
require going to yet higher orders in perturbation theory.  Due to a
combinatorial explosion of the number of diagrams which appear at
increasing orders in the effective theory, however, we need more
systematic methods to compute effective multi-body Hamiltonians at
fourth order.  In any case, we are agnostic as to whether such a
calculation would provide better agreement between experiment and
theory without first performing a detailed analysis of systematic
errors.

@@

The perturbative effective theory developed in Section
\ref{sec:low_energy} is organized in powers of the coupling constants
$G_X$.  The formally small, dimensionless quantities for this
perturbation theory are the two-body interaction energies $K G_X$
divided by the spectral gap $\Delta$ of the non-interacting
Hamiltonian $H_0$.  Here $K$ is a ground-state two-body overlap
integral and $G_X$ is a coupling constant.  The quantities $K$, $G_X$,
and $\Delta$ all depend on the lattice depth $\U$.  Figure
\ref{fig:pert_params} shows these parameters for the case of
${}^{87}$Sr atoms with $X\in\set{\g\g, \e\g_-, \e\g_+, \e\e}$ at
lattice depths $\U\in\sp{30,80}E_{\t{R}}$, where
$E_{\t{R}}\approx3.5\times2\pi~\t{kHz}$ is the lattice photon recoil
energy of the atoms.  The fact that these perturbative parameters grow
with increasing lattice depth $\U$ is a consequence of the fact that
the overlap integral $K$ grows faster with $\U$ than the spectral gap
$\Delta$.  In the case of a harmonic trap with angular frequency
$\omega$, for example, by dimensional analysis these parameters would
be
\begin{align}
  \f{K_{\t{HO}} G_X}{\omega}
  = \f{G_X}{\omega} \int \d^3 x~\abs{\phi_{\t{HO}}}^4
  = \f{G_X}{\omega} \sp{\int \d x~
    \abs{\p{\f{\mA\omega}{\pi}}^{1/4} e^{-\mA\omega x^2/2}}^4}^3
  \propto \sqrt{\omega},
\end{align}
where we assumed that the coupling constants $G_X$ vary weakly with
$\omega$.  While this result may seem to suggest that the low-energy
effective theory should become better at smaller lattice depths,
smaller lattice depths also result in increased theoretical
uncertainties from the growing relevance of the inter-site effects
discussed in Appendix \ref{sec:error}.

@@

When restricted to the subspace of at most one orbital excitation per
lattice site, the $M$-body Hamiltonians of the low-energy effective
theory developed in Section \ref{sec:low_energy} can be written in the
form
\begin{align}
  H_M = \sum_{\abs{\set{\mu_j}}=M}
  \p{U_{M,\g} \n_{\mu_1,\g} \n_{\mu_2,\g}
    + U_{M,+} \n_{\mu_1,\e} \n_{\mu_2,\g}
    + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
    \c_{\mu_2,\g} \c_{\mu_1,\e}}
  \prod_{\alpha=3}^M \n_{\mu_\alpha,\g},
\end{align}
where the coefficients can be expanded as
$U_{MX} = \sum_p U_{MX}^{(p)}$ with terms $U_{MX}^{(p)}$ at order $p$
in the coupling constants $G_Y$.  The terms $U_{MX}^{(p)}$ can be
determined from the $M$-body $p$-order Hamiltonians $H_M^{(p)}$
derived in section \ref{sec:low_energy}, i.e.~in \eqref{eq:H_2},
\eqref{eq:H_3_2}, \eqref{eq:H_3_3}, and \eqref{eq:H_4_3}.  For the
effective 2-, 3-, and 4-body Hamiltonians through third order in the
coupling constants, the coefficients are
\begin{align}
  U_{2,\g} = \f12 \alpha_2^{(1)} G_\g,
  &&
  U_{2,+} = \alpha_2^{(1)} G_+,
  &&
  U_{2,-} = \alpha_2^{(1)} G_-,
\end{align}
\begin{align}
  U_{3,\g}^{(2)} = - \alpha_3^{(2)} G_\g^2,
  &&
  U_{3,+}^{(2)} = - \alpha_3^{(2)} G_+ \p{G_+ + 2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(2)} = - \alpha_3^{(2)} G_- \p{2 G_+ + G_- + 2 G_\g},
\end{align}
\begin{align}
  U_{3,\g}^{(3)}
  = \p{\alpha_3^{(3)} - \alpha_5^{(3)}} 2 G_\g^3
  - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}} G_\g^3,
\end{align}
\begin{align}
  U_{3,+}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} \p{G_+^3 + 4 G_+^2 G_\g
    + G_+ G_-^2 + G_+ G_\g^2 + G_-^3 + G_-^2 G_\g} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  \p{G_+^3 + G_+^2 G_\g + G_+ G_-^2 + G_+ G_\g^2 + G_-^2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} G_- \p{3 G_+^2
    + 2 G_+ G_- + 8 G_+ G_\g + 3 G_- G_\g + G_\g^2} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 2 G_+ G_- + 2 G_+ G_\g + G_-^2 + G_\g^2},
\end{align}
\begin{align}
  U_{4,\g}^{(3)}
  = \p{2\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} G_\g^3
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} 2 G_\g^3,
\end{align}
\begin{align}
  U_{4,+}^{(3)}
  &= \p{2\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_+ G_\g \p{G_+ + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_+ \p{G_+^2 + 2 G_+ G_\g + 5 G_\g^2},
\end{align}
\begin{align}
  U_{4,-}^{(3)}
  &= \p{2\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_- G_\g \p{2 G_+ + G_- + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 3 G_+ G_- + 4 G_+ G_\g + G_-^2
    + 2 G_- G_\g + 5 G_\g^2},
\end{align}
In terms of the spatial overlap integrals defined in \eqref{eq:K_klmn}
and \eqref{eq:K}, the prefactors $\alpha_X^{(p)}$ on the coefficients
$U_X^{(p)}$ are
\begin{align}
  \alpha_2^{(1)} \equiv K,
  &&
  \alpha_3^{(2)} \equiv \sum_{n>0} \f{K_n^2}{E_n},
  &&
  \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
  \f{K_{\ell m} K^m_n K_{\ell n}}{E_{\ell m} E_{\ell n}},
\end{align}
\begin{align}
  \alpha_{4,1}^{(3)}
  \equiv \sum_{\substack{m\ge0\\n>0}} \f{K_{mn} K_m K_n}{E_{mn} E_n},
  &&
  \alpha_{4,2}^{(3)}
  \equiv \sum_{m,n>0} \f{K_m K^m_n K_n}{E_m E_n},
  &&
  \alpha_{4,3}^{(3)}
  \equiv K \sum_{m+n>0} \f{K_{mn}^2}{E_{mn}^2},
\end{align}
\begin{align}
  \alpha_5^{(3)}
  \equiv  K \sum_{n>0} \f{K_n^2}{E_n^2}.
\end{align}
